Phoneme surprisal

### 2019-06-19 surprisal/phoneme_surprisal.Rmd
progress on phoneme surprisal setup

system("rm words.txt phones.txt")
adult_utterances %>%
  distinct(word) %>%
  slice(1:10) %>%
  # filter(word != "", word != "tʃutʃutʃu", word != "ɛː") %>%
  # rowwise() %>%
  # mutate(ipa = get_ipa(word)) 
  pull(word) %>%
  write_lines("words.txt")

system('espeak -f words.txt --ipa=3 -v en-us -q --phonout="phones.txt"')
system("paste -d , words.txt phones.txt > joined.txt")

phones <- read_lines("joined.txt") %>%
  str_split(" ", simplify = F) %>%
  unlist() %>%
  unlist() %>%
  enframe(name = NULL) %>%
  filter(nchar(value) > 0)
phones

adult_phonemes <- adult_utterances %>%
  left_join(ipa) %>%
  unnest_tokens(ipa, word, token = stringr::str_split, pattern = "_", drop = F) %>%
  group_by(utterance_id, word) %>%
  mutate(ipa_order = 1:n()) %>%
  mutate(word_length = max(ipa_order)) %>%
  ungroup()

>>>>

system("rm words.txt phones.txt splitphones.txt joined.csv")
adult_utterances %>%
  distinct(word) %>%
  filter(word != "", word != "tʃutʃutʃu", word != "ɛː", word != "ˈɛ_s") %>%
  # rowwise() %>%
  # mutate(ipa = get_ipa(word)) 
  pull(word) %>%
  write_lines("words.txt")

system("espeak -f words.txt --ipa=3 -v en-us -q --phonout='phones.txt'") #get the ipa of each word
system("cat phones.txt | sed -E 's/ /|/g' | tr '|' '\n' | tail -n +2 > splitphones.txt") #put each ipa word onto its own line in a file called splitphones.txt
system("rm phones.txt")
system("sed '/^$/d' splitphones.txt > phones.txt") #remove empty lines in splitphones
system("paste -d , words.txt phones.txt > joined.csv") #make csv with words and their ipa paired

phones <- read.csv("joined.csv", 
                   header = F, 
                   col.names = c("words", "ipa"))
# phones <- read_lines("joined.txt") %>%
#   str_split(" ", simplify = F) %>%
#   unlist() %>%
#   unlist() %>%
#   enframe(name = NULL) %>%
#   filter(nchar(value) > 0)

adult_phonemes <- adult_utterances %>%
  left_join(phones) %>%
  unnest_tokens(ipa, word, token = stringr::str_split, pattern = "_", drop = F) %>%
  group_by(utterance_id, word) %>%
  mutate(ipa_order = 1:n()) %>%
  mutate(word_length = max(ipa_order)) %>%
  ungroup()
